\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-03-15 presentations/cambridge-18-03-2019/presentation.tex
[Presentation] Update Cambridge '19 presentation

@@

\date{POPL, January 16, 2019}

@@

    % first step: capabilities
    \begin{onlyenv}<+-+(4)>
      \draw[fill=white] (0,2.5) rectangle (6,5.5) node[pos=.5] {\footnotesize current stack frame};
    \end{onlyenv}
    \begin{onlyenv}<.-.(3)>
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack capability };
    \end{onlyenv}
    \begin{onlyenv}<.-.(1)>
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,0) -- (6,16) node (oldframe1) [black,midway,xshift=0.5cm] {};
      \draw (7.5,4) node[right,fill=gray!50] (rp1l) {return capability data};
      \draw (7.4,4.3) pic {lock};
    \end{onlyenv}

    % prepare call: store old return capability
    \begin{onlyenv}<+-+(3)>
      \draw[fill=gray!50] (0,5.5) rectangle node {\tiny old return cap data} (6,6);
      % \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      % (0,0) -- (0,16) node (oldframe1) [black,midway,xshift=-0.5cm] {};
      % \draw (0,5.75) edge[->,out=180,in=225] (oldframe1);
    \end{onlyenv}
    \draw<+-+(2)>[fill=gray!50] (0,6) rectangle node {\tiny old return cap code} (6,6.5);
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=.4},yshift=0pt]
      (6,2.5) -- (6,16) node (callerframe1) [draw=black,pos=.4,xshift=0.8cm] {};
      \draw node[fill=gray!50,right=0cm of callerframe1] (rp1l) {new return capability data};
      \draw ($(rp1l.west) + (-.1,.3)$) pic {lock};
    \end{onlyenv}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] (nsp) { new stack capability };
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Attack on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (20,14) node {\phantom{heap memory}};
    \regfile

    % attacker...
    \begin{onlyenv}<+-+(2)>
      \draw[fill=gray!50] (0,2.5) rectangle (6,6.5) node[pos=.5] {\footnotesize caller stack frame};
      \actadv{(0,6.5)}{(6,9.5)}{callee stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

@@

    % attacker returns
    \begin{onlyenv}<+>
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
      \draw[fill=white] (0,2.5) rectangle (6,6.5) node[pos=.5] {\footnotesize current stack frame};
    \end{onlyenv}

    % attacker gets called again + uses old stack pointer.
    \begin{onlyenv}<+>
      \draw[fill=gray!50] (0,2.5) rectangle (6,10.5) node[pos=.5] {\footnotesize caller stack frame};
      \actadv{(0,10.5)}{(6,13.5)}{callee stack frame}
      \draw (18,8.25) edge[->,color=myred,very thick,out=235,in=0] node[sloped, below] {read/write} (6,8);
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,10.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,2.5) -- (6,16) node (callerframe1) [draw=black,midway,xshift=0.8cm] {};
      % \draw node[fill=gray!50,right=0cm of callerframe1] (rp1l) {return pointer data};
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Linear capabilities}
  \begin{columns}
    \begin{column}{.6\textwidth}
      \begin{tikzpicture}[scale=.45, every node={scale=.5}]
        \scope
          \clip (-.1,-.1) rectangle (6.1,14.9);
          \fill[draw,fill=white] (0,0) rectangle (6,15);
        \endscope
        % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward}
        % (-2,15);
        \foreach \X in {0,0.5,...,14} {
          \fill[draw,fill=white] (0,\X) rectangle (6,\X+.5) node[pos=.5] { };
        };
        \draw (-0.5,0.25) node[align=right] { \scriptsize 0 };
        \draw (-0.5,4.25) node[align=right] { \scriptsize 8 };
        \draw (-0.5,8.25) node[align=right] { \scriptsize 16 };
        \draw (-0.5,12.25) node[align=right] { \scriptsize 24 };

  \begin{scope}
    \clip (11.9,2.6) rectangle (13.6,11.6);
    \foreach \X in {0,1.5,...,7.5} {
      \fill[draw,fill=white] (12,10 - \X) rectangle (13.5,11.5-\X) node[pos=.5] { };
    };
  \end{scope}
  \draw (12.75,12.25) node[align=center] {Register File};
  \draw (6.5,14.325) node[anchor=west, align=left] {Memory}; \draw[->] (-1.5,0) -- (-1.5,4.5);

  % Mem data
  \draw<1-> (3,0.75) node { \scriptsize 42 };
  \draw<1-> (3,1.25) node { \scriptsize 2 };
  \draw<1-> (3,1.75) node { \scriptsize 14 };
  \draw<1-> (3,2.75) node { \scriptsize 10 };
  \draw<1-> (3,2.25) node { \scriptsize 19 };
  \draw<1-> (3,3.75) node { \scriptsize 0 };
  \draw<1-> (3,3.25) node { \scriptsize 0 };
  \draw<1-> (3,4.25) node { \scriptsize 0 };
  \draw<1-> (3,4.75) node { \scriptsize 0 };
  \draw<1-> (3,5.75) node { \scriptsize 3 };
  \draw<1-> (3,6.25) node { \scriptsize 20 };
  \draw<1-> (3,6.75) node { \scriptsize 21 };
  \draw<1-> (3,7.25) node { \scriptsize 11 };
  \draw<1-> (3,7.75) node { \scriptsize 10 };
  \draw<1-> (3,8.25) node { \scriptsize 15 };
  \draw<1-> (3,8.75) node { \scriptsize 19 };
  \draw<1-> (3,9.25) node { \scriptsize 29 };
  \draw<1-> (3,9.75) node { \scriptsize 0 };
  \draw<1-> (3,10.25) node { \scriptsize 0 };
  \draw<1-> (3,10.75) node { \scriptsize 0 };
  \draw<1-> (3,11.25) node { \scriptsize 0 };
  \draw<1-> (3,11.75) node { \scriptsize 0 };
  \draw<1-> (3,12.75) node { \scriptsize 0 };
  \draw<1-> (3,13.25) node { \scriptsize 0 };
  \draw<1-> (3,13.75) node { \scriptsize 64 };
  \draw<1-> (3,14.25) node { \scriptsize 5 };
  % Reg data
  \draw<1-> (12.75,10.75) node { \scriptsize 8 };
  \draw<1-> (12.75,7.75) node { \scriptsize 24 };
  \draw<1-> (12.75,6.25) node { \scriptsize 16 };
  \draw<1-> (12.75,4.75) node { \scriptsize 2 };

  % Mem pointers
  \draw<1> (3,12.25) node { \scriptsize 16 };
  \draw<1> (3,5.25) node { \scriptsize 9 };
  \draw<1> (3,0.25) node { \scriptsize 8 };
  % Reg pointers
  \draw<1> (12.75,9.25) node { \scriptsize 0 };

  % Mem pointers HL
  \draw<2> (3,12.25) node { \color{red} \scriptsize 16 };
  \draw<2> (3,5.25) node { \color{red} \scriptsize 11 };
  \draw<2> (3,0.25) node { \color{red} \scriptsize 8 };
  % Reg pointers HL
  \draw<2> (12.75,9.25) node { \color{red} \scriptsize 0 };

  \draw<3> (12.75,9.25) node { };

  % Mem capabilities
  \draw<4->[capa] (3,12.25) edge[postaction={decorate}] (6.1,12.25 );
  \draw<4> (6.1,12.25) edge[-latex,in=0,out=0] (6.1,8.25);
  \draw<4->[capa] (3,5.25) edge[postaction={decorate}] (6.1,5.25);
  \draw<4> (6.1,5.25) edge[-latex,in=0,out=0] (6.1,6.75);
  \draw<4->[capa] (3,0.25) edge[postaction={decorate}] (6.1,0.25);
  \draw<4> (6.1,0.25) edge[-latex,in=0,out=0] (6.1,4.25);

  % Reg pointers HL
  \draw<4->[capa] (12.75,9.25) edge[postaction={decorate}] (12.0,9.25);
  \draw<4> (12.0,9.25) edge[-latex,in=0,out=180] (6.1,0.25);

  % Mem capabilities \w auth
  \draw<5> (6.1,12.25) edge[-latex,in=0,out=0] (6.5,8.25);
  \draw<5->[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.55,mirror},yshift=0pt] (6.3,5.5) -- (6.3,10.5) node (e) [black,midway,xshift=0.8cm] {};

  \draw<5> (6.1,5.25) edge[-latex,in=0,out=0] (6.3,6.75);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,6) -- (6.1,7.5) node (e) [black,midway,xshift=0.8cm] {};

  \draw<5> (6.1,0.25) edge[-latex,in=0,out=0] (6.5,4.25);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.3,3) -- (6.3,5.5) node (e) [black,midway,xshift=0.8cm] {};

  % Reg pointers HL \w auth
  \draw<5> (12.0,9.25) edge[-latex,in=0,out=180] (6.3,0.355);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.1,mirror},yshift=0pt] (6.1,0) -- (6.1,3.5) node (e) [black,midway,xshift=0.8cm] {};

  % Mem capabilities \w auth & perm
  \draw<6-> (6.1,12.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{r}} (6.5,8.25);

  \draw<6-> (6.1,5.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{rw}} (6.3,6.75);

  \draw<6-> (6.1,0.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{r}} (6.5,4.25);

  % Reg pointers HL \w auth & perm
  \draw<6-> (12.0,9.25) edge[-latex,in=0,out=180] node[right] {\scriptsize \textsc{rx}} (6.3,0.355);
\end{tikzpicture}
\end{column}
\begin{column}{0.4\textwidth}
  \onslide<3->{Replace pointers with capabilities}
  \begin{itemize}
  \item<4-> Pointer
  \item<5-> Range of authority
  \item<6-> Permission
  \end{itemize}
  \onslide<7->{Dynamically enforced}
  \begin{itemize}
  \item<8-> Cap. aware instructions
  \item<9-> Tagged memory
  \end{itemize}
\end{column}
\end{columns}
\end{frame}

@@

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,myred,thick,bend left,dashed] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw (r2) edge[->,myred,thick,bend left, dashed] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,myred,thick,bend left,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw (r1) edge[->,myred,bend left,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return token} };
      \draw node[right=0cm of sp2] (rdp) { return token };
      \draw ($(rdp.west) + (-.1,.3)$) pic {lock};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}
    \draw<.-> (r2) edge[->,myred,bend left,dashed] (sp2);

@@

\begin{frame}
  \frametitle{Paper overview}
\begin{itemize}
\item LCM: A formalization of a simple CHERI-like capability machine with linear capabilities
\item \stktokens{}, a new calling convention that provably guarantees LSE and WBCF on LCM
\item A better way to formalize these guarantees based on a novel technique called \textit{fully-abstract overlay semantics}
\item Proof of LSE and WBCF which includes
  \begin{itemize}
  \item oLCM: an overlay semantics for LCM with built-in LSE and WBCF
  \item proving full-abstraction for the embedding of oLCM into LCM by
  \item defining and using a cross-language, step-indexed, Kripke logical relation with recursive worlds
  \end{itemize}
\end{itemize}
  % \begin{description}
  % \item[Formalization of CHERI-like capability machine with linear capabilities]
  % \item[\stktokens{}] a calling convention that provably guarantees LSE and well-bracketed control-flow WBCF
  % \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  %   \begin{itemize}
  %   \item Proven with cross-language logical relations
  %   \end{itemize}
  %   % TODO Mention the proof and logical relation, move to end?
  % \end{description}
\end{frame}

>>>>

\tikzset{capar/.style={decoration={markings,mark=at position 0 with %
      {\fill[myred] circle(1.5pt);}}}}

\usepackage{tikz-cd}
\pgfdeclarelayer{bg}
\pgfdeclarelayer{mg}
\pgfsetlayers{bg,mg,main}

@@

\date{Cambridge, March, 2019}

@@

    % first step: capabilities
    \begin{onlyenv}<+-+(4)>
      \draw[fill=white] (0,2.5) rectangle (6,5.5) node[pos=.5] {\footnotesize current stack frame};
    \end{onlyenv}
    \begin{onlyenv}<.-.(3)>
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack capability };
      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
    \end{onlyenv}
    \begin{onlyenv}<.-.(1)>
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,0) -- (6,16) node (oldframe1) [black,midway,xshift=0.5cm] {};
      \begin{pgfonlayer}{bg}
        \draw<.-.(1)> (7.5,4) node[right,fill=gray!50] (rp1l) {return capability data};
      \end{pgfonlayer}
      \draw (7.4,4.3) pic {lock};
    \end{onlyenv}

    % prepare call: store old return capability
    \draw<+-+(3)>[fill=gray!50] (0,6) rectangle node {\tiny old return cap code} (6,6.5);
    \begin{onlyenv}<+-+(2)>
      \draw[fill=gray!50] (0,5.5) rectangle node {\tiny old return cap data} (6,6);
      % \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      % (0,0) -- (0,16) node (oldframe1) [black,midway,xshift=-0.5cm] {};
      % \draw (0,5.75) edge[->,out=180,in=225] (oldframe1);
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=.35},yshift=0pt] (6,2.5) -- (6,16) node (callerframe1) [draw=black,pos=.35,xshift=0.8cm] {};
      \begin{pgfonlayer}{bg}
        \draw<.-> node[fill=gray!50,right=0cm of callerframe1] (rp1l) {new return capability data};
      \end{pgfonlayer}
      \draw[capa] (r2) edge[->,postaction={decorate},bend left] (callerframe1);
      \draw ($(rp1l.west) + (-.1,.3)$) pic {lock};
    \end{onlyenv}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] (nsp) { new stack capability };
      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Attack on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \regfile

    % attacker...
    \begin{onlyenv}<+-+(2)>
      \draw[fill=gray!50] (0,2.5) rectangle (6,6.5) node[pos=.5] {\footnotesize caller stack frame};
      \actadv{(0,6.5)}{(6,9.5)}{callee stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};

      \draw node[right=0cm of sp1] { stack pointer };
%      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
    \end{onlyenv}

@@

    % attacker returns
    \begin{onlyenv}<+>
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
      \draw[fill=white] (0,2.5) rectangle (6,6.5) node[pos=.5] {\footnotesize current stack frame};
    \end{onlyenv}

    % attacker gets called again + uses old stack pointer.
    \begin{onlyenv}<+>
      \draw[fill=gray!50] (0,2.5) rectangle (6,10.5) node[pos=.5] {\footnotesize caller stack frame};
      \actadv{(0,10.5)}{(6,13.5)}{callee stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,10.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw[capa] (r1) edge[->,postaction={decorate},bend left] (sp1);
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (18,8.25) edge[->,color=myred,very thick,out=235,in=0,near end] node[sloped, below] {read/write} (6,8);
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,2.5) -- (6,16) node (callerframe1) [draw=black,midway,xshift=0.8cm] {};
      % \draw node[fill=gray!50,right=0cm of callerframe1] (rp1l) {return pointer data};
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Linear capabilities}
  \begin{columns}
    \begin{column}{.6\textwidth}
      \begin{tikzpicture}[scale=.45, every node={scale=.5}]
        \scope
          \clip (-.1,.1) rectangle (6.1,14.9);
          \fill[draw,fill=white] (0,0) rectangle (6,15);
        \endscope
        % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward}
        % (-2,15);
        \foreach \X in {0.5,1,...,14} {
          \fill[draw,fill=white] (0,\X) rectangle (6,\X+.5) node[pos=.5] { };
        };

        \begin{scope}
          \clip (11.9,2.6) rectangle (13.6,11.6);
          \foreach \X in {0,1.5,...,7.5} {
            \fill[draw,fill=white] (12,10 - \X) rectangle (13.5,11.5-\X) node[pos=.5] { };
          };

        \end{scope}
        \coordinate (r1) at (12.75,10.75) {};
        \node[anchor=west] at (13.6,10.75) {$r_1$};
        \coordinate (r2) at (12.75,9.25) {};
        \node[anchor=west] at (13.6,9.25) {$r_2$};
        \coordinate (r3) at (12.75,7.75) {};
        \node[anchor=west] at (13.6,7.75) {$r_3$};
        \coordinate (r4) at (12.75,6.25) {};
        \node[anchor=west] at (13.6,6.25) {$r_4$};

        \draw (12.75,12.25) node[align=center] {Register File};
        \draw (6.5,14.325) node[anchor=west, align=left] {Memory};

        % move
        \draw<1-2>[capa] (r2) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,11.25);
        \draw<1-5>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,10) -- (6.1,12.5) node (e) [black,midway,xshift=0.8cm] {};
        \draw<3-4>[capa] (r1) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,11.25);
        \node<3> at (r2) {0};

        % store 
        \draw<4-5>[capa] (r4) edge[->,postaction={decorate},out=180,in=0] node[above] {\tiny\textsc{rw}} (6.3,7.75);
        \draw<4-5>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,6.5) -- (6.1,9) node (e) [black,midway,xshift=0.8cm] {};
        \draw<5>[capa] (3,8.25) edge[postaction={decorate},dashed] (6.3,8.25);
        \draw<5> (6.3,8.25) edge[->,out=0,in=0,dashed] (6.3,11.25);
        \node<5> at (r1) {0};

        % split
        \draw<6>[capa] (r3) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,10);
        \draw<6>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,7.5) -- (6.1,12.5) node (e) [black,midway,xshift=0.8cm] {};

        \draw<7-8>[capa] (r2) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,8.75);
        \draw<7-8>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,7.5) -- (6.1,10) node (e) [black,midway,xshift=0.8cm] {};
        \draw<7-8>[capa] (r1) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,11.25);
        \draw<7-8>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,10) -- (6.1,12.5) node (e) [black,midway,xshift=0.8cm] {};
        \node<7-8> at (r3) {0};

        % splice
        \draw<9>[capa] (r3) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,10);
        \draw<9>[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,7.5) -- (6.1,12.5) node (e) [black,midway,xshift=0.8cm] {};

        \node<9> at (r1) {0};
        \node<9> at (r2) {0};

        % splice fail
        \draw<10->[capa] (r1) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,11.25);
        \draw<10->[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,10) -- (6.1,12.5) node (e) [black,midway,xshift=0.8cm] {};
        \draw<10->[capa] (r2) edge[->,postaction={decorate},out=180,in=0,dashed] (6.3,7.75);
        \draw<10->[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,6.5) -- (6.1,9) node (e) [black,midway,xshift=0.8cm] {};

        \draw<11>[mygreen,very thick] (5.6,10) -- (6.6,9);
        \draw<11>[mygreen,very thick] (5.6,9) -- (6.6,10);
        \draw<11> node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, anchor=west] () at (7,9.5) { Splice fails};

      \end{tikzpicture}
    \end{column}
\begin{column}{0.4\textwidth}
  \onslide<1->{Linear capabilities}
  \begin{itemize}
  \item<1-> Non-duplicable
  \item<2-> \texttt{move $r_1$ $r_2$}
  \item<4-> \texttt{store $r_4$ $r_1$}
  \item<6-> \texttt{split $r_1$ $r_2$ $r_3$ $n$}
  \item<8-> \texttt{splice $r_3$ $r_1$ $r_2$}
  \end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Call with \stktokens{}}
  % Emphazise that it is dynamically enforced.
  % Other cases, see paper.
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (20,14) node {\phantom{heap memory}};

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw[capar] (r1) edge[->,myred,thick,bend left,dashed,postaction={decorate}] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw[capar] (r2) edge[->,myred,thick,bend left, dashed,postaction={decorate}] (sp2);
      \draw node[right=0cm of sp2] { private stack pointer };
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw[capar] (r1) edge[->,myred,thick,bend left,dashed,postaction={decorate}] (usp);
      \draw node[right=0cm of usp] { stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>

      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return token} };
      \draw node[right=0cm of sp2] (rdp) { return token };
      \draw ($(rdp.west) + (-.1,.3)$) pic {lock};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actsf{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}
    \begin{onlyenv}<.-.(1)>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
    \draw[capar] (r2) edge[->,myred,bend left,dashed,postaction={decorate}] (sp2);

    \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
    \draw[capar] (r1) edge[->,myred,bend left,dashed,postaction={decorate}] (usp);
    \draw node[right=0cm of usp] { stack pointer };
    \end{onlyenv}

    % Return from callee
    \begin{onlyenv}<+>
      \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    \begin{onlyenv}<+>
      \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw[capar] (r1) edge[->,myred,thick,bend left,dashed,postaction={decorate}] (sp1);
    \end{onlyenv}
  \end{tikzpicture}  
\end{frame}

@@

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace[sp1]{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw[capar] (r1) edge[->,myred,thick,bend left,dashed,postaction={decorate}] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw[capar] (r2) edge[->,myred,thick,bend left, dashed,postaction={decorate}] (sp2);
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt] (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw[capar] (r1) edge[->,myred,thick,bend left,dashed,postaction={decorate}] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw [decorate,decoration={brace,aspect=0.2,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,5) -- (6.5,16) node[draw=black] (usp) [black,pos=0.2,xshift=0.8cm] {};
      \draw[capar] (r1) edge[->,myred,bend left,dashed,postaction={decorate}] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw node[fill=gray,opacity=0.5, right=0cm of sp2] { \phantom{return token} };
      \draw node[right=0cm of sp2] (rdp) { return token };
      \draw ($(rdp.west) + (-.1,.3)$) pic {lock};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}
    \draw<.->[capar] (r2) edge[->,myred,bend left,dashed,postaction={decorate}] (sp2);

@@

\begin{frame}
  \frametitle{Full abstraction}
  \begin{theorem}[Full abstraction]
  For \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (rea) {reasonable};, \tikz[remember picture] \node[inner sep=0pt, outer sep=0pt] (wf) {well-formed};\ $\comp_1$ and $\comp_2$, we have
  \begin{gather*}
    \src{\comp_1} \sconeq \src{\comp_2} \quad \Leftrightarrow \quad    \src{\comp_1} \tconeq \src{\comp_2} \qedhere
  \end{gather*}
\end{theorem}
\vspace{-0.5cm}
\rule{1\textwidth}{0.4pt}
\begin{columns}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<3->]
    \item \stktokens{} reasonable use of return seals
      \begin{itemize}
      \item Return seals are only used to seal old program pointers.
      \item Every return seal is only used for one call site.
      \item Return seals are not leaked.
      \end{itemize}
    \item<4-> No measures against us
  \end{itemize}
  \end{column}
  \begin{column}{0.5\textwidth}
    \begin{itemize}[<6->]
    \item Component structure.
    \item Sane linker behaviour.
    \end{itemize}
  \end{column}
\end{columns}
\vspace{0.5cm}
\onslide<7>{\centering Should be handled in earlier compiler phase}
\begin{tikzpicture}[remember picture, overlay]
  \draw<2-4> node[rectangle, fit=(rea), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
  \draw<5> node[rectangle, fit=(wf), draw=myred, rounded corners, inner sep=2pt, yshift=-1pt, xshift=0.75pt] (n1) {};
\end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{Conclusion}
\begin{itemize}
\item \stktokens{} ensures well-bracketed control flow and local-state encapsulation.
\item Overlay semantics used to define well-bracketed calls and local state encapsulation.
\item Capability machines may be a good target for secure compilation.
\end{itemize}
  % \begin{description}
  % \item[Formalization of CHERI-like capability machine with linear capabilities]
  % \item[\stktokens{}] a calling convention that provably guarantees LSE and well-bracketed control-flow WBCF
  % \item[Fully-abstract overlay semantics] a novel way to prove LSE and WBCF claims
  %   \begin{itemize}
  %   \item Proven with cross-language logical relations
  %   \end{itemize}
  %   % TODO Mention the proof and logical relation, move to end?
  % \end{description}
\end{frame}
